---
title: "ACS vs ACM"
output: html_notebook
---

Loading the libraries

```{r}
library(FactoClass)
library(FactoMineR)
library(tidyverse)
```

Loading data

```{r}
data("admi")
head(admi)
```

Doing ACS

```{r}
# Preparing the data for do a CA 

carr <- admi$carr
estr <- admi$estr

admi_CA <- as.data.frame(cbind(carr,estr))

# Performing an CA

ACS <- CA(admi_CA)


```

Doing MCA

```{r}

# Preparing an ACM to to MCA
admi_ACM<-  admi %>% select(carr,estr)

# performing a MCA
ACM <- MCA(admi_ACM)

```

Disjunctive table

```{r}
disjunctive <- tab.disjonctif.prop(admi_ACM,seed=NULL,row.w=NULL)
head(disjunctive)

```
number of rows disjuntive table

```{r}
nrow(disjunctive)
```

number of col disjuntive table
```{r}

ncol(disjunctive)
```

number of dimentions MCA

```{r}
summary(ACM)

```


Burt table

```{r}
library(GDAtools)
burt_table <- burt(admi_ACM)
```

number of rows burt table

```{r}

nrow(burt_table)

```

number of columns burt table

```{r}

ncol(burt_table)
```


variance by dimentions MCA

```{r}

variance <- ACM$eig[,2]
variance
```

Acumulative variance

```{r}
variance_acum <- ACM$eig[,3]
variance_acum
```

HomeWork_code

```{r}

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
